---
title: "Intrinsic Data Liquidity and Realized Liquidity: Empirical Report"
subtitle: "Main Specification (Poisson) + Configurational Robustness (fsQCA)"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    fig_width: 7
    fig_height: 5
    fig_caption: true
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = FALSE,
  message    = FALSE,
  warning    = FALSE,
  fig.align  = "center",
  out.width  = "85%",
  dpi        = 300,
  cache      = FALSE
)

suppressPackageStartupMessages({
  library(jsonlite)
  library(dplyr)
  library(tidyr)
  library(stringr)
  library(ggplot2)
  library(scales)
  library(fixest)
  library(QCA)
  library(kableExtra)
})

theme_set(
  theme_minimal(base_size = 12) +
    theme(
      panel.grid.minor = element_blank(),
      plot.title       = element_text(face = "bold", size = 13),
      plot.subtitle    = element_text(size = 10, color = "grey40"),
      legend.position  = "bottom"
    )
)
```

# Data Construction

## Loading and Deduplication

```{r load-data}
source("datarade_helpers.R")

data_path <- file.path("data", "updated_datarade_data_scored_copy.jsonl")
if (!file.exists(data_path)) data_path <- "updated_datarade_data_scored_copy.jsonl"
if (!file.exists(data_path)) stop("Data file not found: updated_datarade_data_scored_copy.jsonl")

lines <- readLines(data_path, warn = FALSE)
raw   <- lapply(lines, function(l) tryCatch(fromJSON(l), error = function(e) NULL))
raw   <- raw[!sapply(raw, is.null)]
urls  <- sapply(raw, function(r) r[["url"]] %||% NA_character_)
raw   <- raw[!duplicated(urls)]

df <- tibble(
  url = sapply(raw, function(r) r[["url"]] %||% NA_character_),
  provider_url = sapply(raw, function(r) {
    v <- r[["provider_url"]]
    if (is.null(v) || length(v) == 0) NA_character_ else as.character(v[1])
  }),
  # --- Clarity: continuous score + binary prediction ---
  C_score   = sapply(raw, function(r) as.numeric(r[["semantic_score"]] %||% NA_real_)),
  c_semantic = sapply(raw, function(r) as.integer(r[["semantic_pred"]] %||% NA_integer_)),
  # --- Temporal & Composability ---
  t_rank = sapply(raw, function(r)
    temporal_rank_full(r[["delivery"]], r[["details"]], r[["history"]])),
  k_hard_key_count = sapply(raw, function(r)
    hard_key_count_from_dd(r[["data_dictionary"]])),
  # --- Outcomes ---
  payment_modality      = sapply(raw, function(r)
    payment_modality_displayed(r[["pricing_plans"]])),
  price_displayed       = sapply(raw, function(r)
    price_displayed_from_metadata(r[["pricing_plans"]])),
  free_sample_available = sapply(raw, function(r)
    has_free_sample_offer(r[["details"]], r[["history"]],
                          r[["product-content__pricing-info"]], r[["delivery"]])),
  api_method            = sapply(raw, function(r) has_api_method(r[["delivery"]])),
  # --- Provider controls ---
  provider_rating = sapply(raw, function(r) {
    v <- r[["provider__rating-summary-score"]]
    if (is.null(v) || length(v) == 0 || !nzchar(as.character(v))) return(NA_real_)
    as.numeric(v[1])
  }),
  # --- Use-case tags ---
  use_cases = lapply(raw, function(r) {
    uc <- r[["use_cases"]]
    if (is.null(uc) || length(uc) == 0) return(character(0))
    as.character(unlist(uc))
  })
)
```

## Variable Construction

Semantic clarity is measured by the **continuous classifier score** ($C_i^{\text{score}} \in [0.25,\,0.77]$)
produced by the LLM-based semantic classifier (Gabriel).  This score reflects the
probability that a listing's content qualifies as semantically clear under the
ostension/transformation/contamination decision rules.  We also retain the binary
prediction ($C_i^{\text{pred}} \in \{0,1\}$, threshold $\approx 0.52$) for
comparison in the fsQCA.

Temporal intensity and composability use the same continuous operationalisations
as the main paper: cadence rank (0–9) and $\log(1 + \text{hard\_key\_count})$.

```{r construct-variables}
df <- df %>% mutate(
  # Continuous conditions
  T_rank   = pmax(t_rank, 0L),                                       # 0–9
  K_log    = log1p(k_hard_key_count),                                 # 0–~5
  # Outcome count
  across(c(payment_modality, price_displayed, free_sample_available, api_method),
         ~replace_na(., 0L)),
  liquidity_count = payment_modality + price_displayed +
    free_sample_available + api_method,                               # 0–4
  # Legacy binary
  J_i = as.integer(c_semantic == 1 & T_rank >= 5 & k_hard_key_count >= 1)
)

# IDL composite (standardised)
df <- df %>% mutate(
  IDL_raw = scale(C_score)[,1] + scale(T_rank)[,1] + scale(K_log)[,1],
  IDL_std = as.numeric(scale(IDL_raw))
)

# Provider n (listing count)
prov_n <- df %>% count(provider_url, name = "provider_n")
df <- left_join(df, prov_n, by = "provider_url") %>%
  mutate(
    provider_n = replace_na(provider_n, 1L),
    rating_missing  = as.integer(is.na(provider_rating)),
    provider_rating = replace_na(provider_rating, 0)
  )

# Use-case dummies (≥2 occurrences)
uc_long <- df %>%
  mutate(row = row_number()) %>%
  unnest(use_cases) %>%
  mutate(use_cases = str_to_lower(str_squish(use_cases))) %>%
  filter(nzchar(use_cases))
uc_freq <- uc_long %>% count(use_cases) %>% filter(n >= 2)
uc_wide <- uc_long %>%
  filter(use_cases %in% uc_freq$use_cases) %>%
  mutate(v = 1L) %>%
  pivot_wider(id_cols = row, names_from = use_cases, values_from = v,
              values_fill = 0L, names_prefix = "uc_")
df <- df %>% mutate(row = row_number()) %>%
  left_join(uc_wide, by = "row") %>%
  dplyr::select(-row)
uc_cols <- grep("^uc_", names(df), value = TRUE)
df <- df %>% mutate(across(all_of(uc_cols), ~replace_na(., 0L)))

# Sanitise use-case column names: replace spaces/special chars with underscores
safe_names <- make.names(uc_cols)
names(df)[names(df) %in% uc_cols] <- safe_names
uc_cols <- safe_names

# IDL quintile
df$IDL_Q <- cut(df$IDL_std,
                breaks = quantile(df$IDL_std, probs = 0:5/5, na.rm = TRUE),
                include.lowest = TRUE, labels = paste0("Q", 1:5))

N_obs <- nrow(df)
N_prov <- n_distinct(df$provider_url)
N_uc   <- length(uc_cols)
```

The sample contains **`r format(N_obs, big.mark=",")`** unique product listings
from **`r N_prov`** providers, with **`r N_uc`** use-case control dummies.

| Symbol | Measure | Range | Construction |
|--------|---------|------:|--------------|
| $C_i$ | Semantic clarity | [0.25, 0.77] | LLM classifier probability (`semantic_score`) |
| $T_i$ | Temporal intensity | 0–9 | Maximum cadence rank (historical=0 … real-time=9) |
| $K_i$ | Composability | 0–~5 | $\log(1 + \text{hard\_key\_count})$ |
| $\text{IDL}_i$ | Composite index | continuous | Standardised sum of $z(C_i) + z(T_i) + z(K_i)$ |
| $Y_i$ | Realized liquidity | 0–4 | Sum of four transactional-readiness signals |

# Descriptive Statistics

## Summary Statistics

```{r tbl-summary}
summ <- df %>%
  summarise(
    across(c(C_score, T_rank, K_log, IDL_std, liquidity_count,
             payment_modality, price_displayed, free_sample_available, api_method,
             provider_n, provider_rating),
           list(
             Mean = ~mean(., na.rm = TRUE),
             SD   = ~sd(., na.rm = TRUE),
             Min  = ~min(., na.rm = TRUE),
             Med  = ~median(., na.rm = TRUE),
             Max  = ~max(., na.rm = TRUE)
           ), .names = "{.col}__{.fn}")
  ) %>%
  pivot_longer(everything(),
               names_to = c("Variable", ".value"),
               names_sep = "__")

var_labels <- c(
  C_score   = "Semantic Clarity (C)",
  T_rank    = "Temporal Intensity (T)",
  K_log     = "Composability (K)",
  IDL_std   = "IDL Index (std.)",
  liquidity_count   = "Liquidity Count (Y)",
  payment_modality  = "Payment Modality",
  price_displayed   = "Price Displayed",
  free_sample_available = "Free Sample",
  api_method        = "API Delivery",
  provider_n        = "Provider Listing Count",
  provider_rating   = "Provider Rating"
)
summ$Variable <- var_labels[summ$Variable]

kbl(summ, digits = 3, col.names = c("Variable", "Mean", "SD", "Min", "Median", "Max"),
    caption = "Table 1 — Summary Statistics (N = 4,552)") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  pack_rows("IDL Conditions", 1, 4) %>%
  pack_rows("Outcomes", 5, 9) %>%
  pack_rows("Controls", 10, 11)
```

## Correlation Matrix

```{r tbl-corr}
cor_vars <- df %>% dplyr::select(C_score, T_rank, K_log, IDL_std, liquidity_count)
cor_mat  <- cor(cor_vars, use = "pairwise.complete.obs")

# Pretty labels
rownames(cor_mat) <- colnames(cor_mat) <- c("C", "T", "K", "IDL", "Y")

kbl(round(cor_mat, 3),
    caption = "Table 2 — Pairwise Correlations") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE)
```

## IDL Quintile Gradient

```{r fig-quintile, fig.cap="Figure 1 — Mean Realized Liquidity by IDL Quintile"}
q_means <- df %>%
  filter(!is.na(IDL_Q)) %>%
  group_by(IDL_Q) %>%
  summarise(
    mean_liq = mean(liquidity_count),
    se       = sd(liquidity_count) / sqrt(n()),
    n        = n(),
    .groups  = "drop"
  )

ggplot(q_means, aes(x = IDL_Q, y = mean_liq)) +
  geom_col(fill = "#2c7fb8", width = 0.65) +
  geom_errorbar(aes(ymin = mean_liq - 1.96 * se, ymax = mean_liq + 1.96 * se),
                width = 0.2) +
  geom_text(aes(label = sprintf("%.2f", mean_liq)), vjust = -1.5, size = 3.5) +
  scale_y_continuous(expand = expansion(mult = c(0, .15))) +
  labs(x = "IDL Quintile", y = "Mean Liquidity Count (0–4)") +
  theme(panel.grid.major.x = element_blank())
```

# Main Specification: Poisson Regression {.tabset}

## Model

The outcome $Y_i \in \{0,1,2,3,4\}$ counts how many transactional-readiness
signals a listing activates.  Because the outcome is a bounded count with
moderate overdispersion, we estimate a **Poisson pseudo-maximum-likelihood**
model with heteroskedasticity-robust standard errors:

$$
E[Y_i \mid \mathbf{X}_i] = \exp\!\Big(\alpha + \beta\,\text{IDL}_i^{\text{std}}
  + \gamma_1\,\text{provider\_n}_i + \gamma_2\,\text{provider\_rating}_i
  + \gamma_3\,\mathbf{1}_{\text{rating missing}}
  + \sum_{u \in \mathcal{U}} \delta_u\, U_{iu}\Big)
$$

The coefficient $\beta$ is interpreted as an **incidence-rate ratio (IRR)**:
$e^\beta$ gives the multiplicative change in expected liquidity count for a
one-standard-deviation increase in the IDL index.

```{r main-poisson}
fml_main <- as.formula(
  paste0("liquidity_count ~ IDL_std + provider_n + provider_rating + rating_missing + ",
         paste(uc_cols, collapse = " + "))
)

m_pois <- fepois(fml_main, data = df, vcov = "hetero")

# Extract key stats
coefs <- coeftable(m_pois)
b     <- coefs["IDL_std", "Estimate"]
se_b  <- coefs["IDL_std", "Std. Error"]
z_b   <- coefs["IDL_std", "z value"]
p_b   <- coefs["IDL_std", "Pr(>|z|)"]
irr   <- exp(b)
irr_lo <- exp(b - 1.96 * se_b)
irr_hi <- exp(b + 1.96 * se_b)
n_obs <- nobs(m_pois)
ll    <- logLik(m_pois)
pr2   <- 1 - as.numeric(ll) / as.numeric(logLik(fepois(liquidity_count ~ 1, data = df)))
```

## Results

```{r tbl-main-result}
main_tbl <- tibble(
  ` ` = c("IDL (std.)", "", "Provider listing count", "Provider rating",
          "Use-case dummies", "Observations", "Pseudo R²"),
  `Coefficient` = c(
    sprintf("%.4f", b), sprintf("(%.4f)", se_b),
    sprintf("%.4f", coefs["provider_n", "Estimate"]),
    sprintf("%.4f", coefs["provider_rating", "Estimate"]),
    paste0(N_uc, " included"),
    format(n_obs, big.mark = ","),
    sprintf("%.4f", pr2)
  ),
  `IRR` = c(
    sprintf("%.3f", irr), "",
    sprintf("%.3f", exp(coefs["provider_n", "Estimate"])),
    sprintf("%.3f", exp(coefs["provider_rating", "Estimate"])),
    "", "", ""
  ),
  `95% CI` = c(
    sprintf("[%.3f, %.3f]", irr_lo, irr_hi), "",
    "", "", "", "", ""
  ),
  `p` = c(
    ifelse(p_b < 0.001, "< .001", sprintf("%.3f", p_b)), "",
    ifelse(coefs["provider_n", "Pr(>|z|)"] < 0.001, "< .001",
           sprintf("%.3f", coefs["provider_n", "Pr(>|z|)"])),
    ifelse(coefs["provider_rating", "Pr(>|z|)"] < 0.001, "< .001",
           sprintf("%.3f", coefs["provider_rating", "Pr(>|z|)"])),
    "", "", ""
  )
)

kbl(main_tbl,
    caption = "Table 3 — Main Specification: Poisson Regression of Liquidity Count on IDL",
    align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  footnote(general = "Poisson PML with Huber–White robust SEs. Use-case dummies retained if ≥ 2 occurrences (503 controls).")
```

**Interpretation.** A one-standard-deviation increase in the IDL index
raises the expected number of transactional-readiness signals by a factor
of **`r sprintf("%.3f", irr)`** (IRR, 95% CI [`r sprintf("%.3f", irr_lo)`,
`r sprintf("%.3f", irr_hi)`], *p* < .001).

## Disaggregated Effects

```{r disagg-poisson}
fml_disagg <- as.formula(
  paste0("liquidity_count ~ C_score + T_rank + K_log + provider_n + provider_rating + rating_missing + ",
         paste(uc_cols, collapse = " + "))
)
m_disagg <- fepois(fml_disagg, data = df, vcov = "hetero")
cd <- coeftable(m_disagg)

disagg_tbl <- tibble(
  Condition = c("Semantic Clarity (C)", "Temporal Intensity (T)", "Composability (K)"),
  Coef      = sprintf("%.4f", cd[c("C_score", "T_rank", "K_log"), "Estimate"]),
  SE        = sprintf("(%.4f)", cd[c("C_score", "T_rank", "K_log"), "Std. Error"]),
  IRR       = sprintf("%.3f", exp(cd[c("C_score", "T_rank", "K_log"), "Estimate"])),
  p         = ifelse(cd[c("C_score", "T_rank", "K_log"), "Pr(>|z|)"] < 0.001,
                     "< .001",
                     sprintf("%.3f", cd[c("C_score", "T_rank", "K_log"), "Pr(>|z|)"]))
)

kbl(disagg_tbl,
    caption = "Table 4 — Disaggregated Poisson: Individual IDL Components",
    align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  footnote(general = "Same specification as Table 3, replacing IDL composite with its three components. All three contribute positively and significantly.")
```

# Robustness: Regression Variants

```{r robustness-regressions}
# 1. OLS
fml_ols <- fml_main
m_ols <- feols(fml_ols, data = df, vcov = "hetero")
ols_b  <- coeftable(m_ols)["IDL_std", "Estimate"]
ols_se <- coeftable(m_ols)["IDL_std", "Std. Error"]
ols_p  <- coeftable(m_ols)["IDL_std", "Pr(>|t|)"]

# 2. Ordered logit
m_ologit <- MASS::polr(ordered(liquidity_count) ~ IDL_std + provider_n + provider_rating + rating_missing,
                        data = df, method = "logistic", Hess = TRUE)
ologit_coefs <- summary(m_ologit)$coefficients
ologit_b  <- ologit_coefs["IDL_std", "Value"]
ologit_se <- ologit_coefs["IDL_std", "Std. Error"]
ologit_t  <- ologit_coefs["IDL_std", "t value"]
ologit_p  <- 2 * pnorm(-abs(ologit_t))

# 3. Provider FE Poisson
m_pfe <- fepois(liquidity_count ~ IDL_std + provider_n + provider_rating + rating_missing | provider_url,
                data = df, vcov = "hetero")
pfe_b  <- coeftable(m_pfe)["IDL_std", "Estimate"]
pfe_se <- coeftable(m_pfe)["IDL_std", "Std. Error"]
pfe_p  <- coeftable(m_pfe)["IDL_std", "Pr(>|z|)"]

# 4. No use-case controls
m_nouc <- fepois(liquidity_count ~ IDL_std + provider_n + provider_rating + rating_missing,
                 data = df, vcov = "hetero")
nouc_b  <- coeftable(m_nouc)["IDL_std", "Estimate"]
nouc_se <- coeftable(m_nouc)["IDL_std", "Std. Error"]
nouc_p  <- coeftable(m_nouc)["IDL_std", "Pr(>|z|)"]

# 5. Binary J_i (legacy union indicator)
fml_ji <- as.formula(
  paste0("liquidity_count ~ J_i + provider_n + provider_rating + rating_missing + ",
         paste(uc_cols, collapse = " + "))
)
m_ji <- fepois(fml_ji, data = df, vcov = "hetero")
ji_b  <- coeftable(m_ji)["J_i", "Estimate"]
ji_se <- coeftable(m_ji)["J_i", "Std. Error"]
ji_p  <- coeftable(m_ji)["J_i", "Pr(>|z|)"]

# 6. Above-median binary
df$IDL_high <- as.integer(df$IDL_std > 0)
fml_bin <- as.formula(
  paste0("liquidity_count ~ IDL_high + provider_n + provider_rating + rating_missing + ",
         paste(uc_cols, collapse = " + "))
)
m_bin <- fepois(fml_bin, data = df, vcov = "hetero")
bin_b  <- coeftable(m_bin)["IDL_high", "Estimate"]
bin_se <- coeftable(m_bin)["IDL_high", "Std. Error"]
bin_p  <- coeftable(m_bin)["IDL_high", "Pr(>|z|)"]

# 7. IDL quintile dummies
df$IDL_Q2 <- relevel(factor(df$IDL_Q), ref = "Q1")
fml_q <- as.formula(
  paste0("liquidity_count ~ IDL_Q2 + provider_n + provider_rating + rating_missing + ",
         paste(uc_cols, collapse = " + "))
)
m_q <- fepois(fml_q, data = df, vcov = "hetero")
q5_b  <- coeftable(m_q)["IDL_Q2Q5", "Estimate"]
q5_se <- coeftable(m_q)["IDL_Q2Q5", "Std. Error"]
q5_p  <- coeftable(m_q)["IDL_Q2Q5", "Pr(>|z|)"]

fmt_p <- function(p) ifelse(p < 0.001, "< .001", sprintf("%.3f", p))

rob_tbl <- tibble(
  Specification = c(
    "(1) OLS",
    "(2) Ordered Logit (no UC FE)",
    "(3) Poisson + Provider FE",
    "(4) Poisson, no UC controls",
    "(5) Binary J_i (legacy)",
    "(6) Above-median IDL",
    "(7) Q5 vs Q1 (quintile dummies)"
  ),
  Estimate = c(
    sprintf("%.3f", ols_b),
    sprintf("%.3f", ologit_b),
    sprintf("%.3f", pfe_b),
    sprintf("%.3f", nouc_b),
    sprintf("%.3f", ji_b),
    sprintf("%.3f", bin_b),
    sprintf("%.3f", q5_b)
  ),
  SE = c(
    sprintf("(%.3f)", ols_se),
    sprintf("(%.3f)", ologit_se),
    sprintf("(%.3f)", pfe_se),
    sprintf("(%.3f)", nouc_se),
    sprintf("(%.3f)", ji_se),
    sprintf("(%.3f)", bin_se),
    sprintf("(%.3f)", q5_se)
  ),
  `IRR / OR` = c(
    "—",
    sprintf("%.3f", exp(ologit_b)),
    sprintf("%.3f", exp(pfe_b)),
    sprintf("%.3f", exp(nouc_b)),
    sprintf("%.3f", exp(ji_b)),
    sprintf("%.3f", exp(bin_b)),
    sprintf("%.3f", exp(q5_b))
  ),
  p = c(fmt_p(ols_p), fmt_p(ologit_p), fmt_p(pfe_p), fmt_p(nouc_p),
        fmt_p(ji_p), fmt_p(bin_p), fmt_p(q5_p))
)

kbl(rob_tbl,
    caption = "Table 5 — Robustness: Alternative Regression Specifications",
    align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  footnote(general = c(
    "Row 1: OLS with robust SEs, coefficient is β.",
    "Row 2: Ordered logit without use-case FE, shows OR.",
    "Rows 3–7: Poisson PML with robust SEs, shows IRR.",
    "All specifications include provider controls. UC dummies included except rows 2,3,4."
  ))
```

All seven alternative specifications return a **positive and statistically
significant** association between IDL and realized liquidity.

## Quintile Gradient Detail

```{r fig-quintile-outcomes, fig.cap="Figure 2 — Outcome Prevalence by IDL Quintile"}
q_out <- df %>%
  filter(!is.na(IDL_Q)) %>%
  group_by(IDL_Q) %>%
  summarise(
    `Payment Modality` = mean(payment_modality),
    `Price Displayed`  = mean(price_displayed),
    `Free Sample`      = mean(free_sample_available),
    `API Delivery`     = mean(api_method),
    .groups = "drop"
  ) %>%
  pivot_longer(-IDL_Q, names_to = "Outcome", values_to = "Prevalence")

ggplot(q_out, aes(x = IDL_Q, y = Prevalence, fill = Outcome)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.65) +
  scale_y_continuous(labels = percent_format(), expand = expansion(mult = c(0, .08))) +
  scale_fill_brewer(palette = "Set2") +
  labs(x = "IDL Quintile", y = "Outcome Prevalence (%)") +
  theme(panel.grid.major.x = element_blank())
```

# Robustness: Fuzzy-Set Qualitative Comparative Analysis (fsQCA)

The fsQCA provides a **configurational complement** to the regression analysis.
While Poisson regression estimates the *average marginal effect* of the IDL
index on liquidity count, fsQCA tests whether specific **combinations of
conditions** (C, T, K) are **set-theoretically sufficient** to produce high
realized liquidity.  The two approaches operate under fundamentally different
logics:

| | Regression | fsQCA |
|-----|:-----------|:------|
| Question | Does more IDL produce more signals *on average*? | Is C·T·K a reliable *recipe* for high liquidity? |
| Logic | Symmetric, net-effect | Asymmetric, set-theoretic |
| Equifinality | Not modelled | Explicitly identified |
| Causal asymmetry | Assumed symmetric | ~C·~T·~K need not explain ~Y |

## Fuzzy Calibration

Continuous measures are transformed into fuzzy-set membership scores $\in [0,1]$
using direct calibration with three qualitative anchors (fully out, crossover,
fully in).  We compare two operationalisations of semantic clarity:

- **C~old~**: the binary NLP prediction (`semantic_pred` ∈ {0, 1}), used as crisp set.
- **C~new~**: the continuous classifier score (`semantic_score` ∈ [0.25, 0.77]), calibrated as fuzzy set.

```{r fsqca-calibration}
# Calibrate
df$fs_C_old <- as.numeric(df$c_semantic)  # crisp 0/1

# C_new: continuous score.  Anchors chosen from distribution:
#   fully-out = 0.30 (~5th pct), crossover = 0.52 (threshold), fully-in = 0.73 (~95th pct)
df$fs_C_new <- calibrate(df$C_score, type = "fuzzy", thresholds = c(0.30, 0.52, 0.73))
df$fs_T     <- calibrate(df$T_rank,  type = "fuzzy", thresholds = c(0, 4, 9))
df$fs_K     <- calibrate(df$k_hard_key_count, type = "fuzzy", thresholds = c(0, 1, 5))
df$fs_OUT   <- calibrate(df$liquidity_count,  type = "fuzzy", thresholds = c(0, 2, 4))

# Standard nudge: 0.5 → 0.501 to resolve crossover ambiguity
nudge <- function(x) ifelse(x == 0.5, x + 0.001, x)
df$fs_C_new <- nudge(df$fs_C_new)
df$fs_T     <- nudge(df$fs_T)
df$fs_K     <- nudge(df$fs_K)
df$fs_OUT   <- nudge(df$fs_OUT)

cal_tbl <- tibble(
  Set = c("C (NLP prediction, crisp)", "C (classifier score, fuzzy)",
          "T (temporal)", "K (composability)", "Y (liquidity)"),
  `Raw measure` = c("semantic_pred {0,1}", "semantic_score [0.25–0.77]",
                     "T_rank (0–9)", "hard_key_count", "liquidity_count (0–4)"),
  `Fully out` = c(0, 0.30, 0, 0, 0),
  Crossover   = c("—", 0.52, 4, 1, 2),
  `Fully in`  = c(1, 0.73, 9, 5, 4),
  `Mean fs`   = c(mean(df$fs_C_old), mean(df$fs_C_new), mean(df$fs_T),
                  mean(df$fs_K), mean(df$fs_OUT))
)

kbl(cal_tbl, digits = 3,
    caption = "Table 6 — Fuzzy-Set Calibration Anchors and Summary") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  footnote(general = "Direct calibration using QCA::calibrate(). C_new anchors: 5th percentile (fully out), classifier threshold (crossover), 95th percentile (fully in). Cases at 0.5 nudged +0.001.")
```

## Necessity Analysis

A condition is **necessary** for an outcome if its consistency score ≥ 0.90.

```{r fsqca-necessity}
qca_old <- data.frame(C = df$fs_C_old, T = df$fs_T, K = df$fs_K, OUT = df$fs_OUT)
qca_new <- data.frame(C = df$fs_C_new, T = df$fs_T, K = df$fs_K, OUT = df$fs_OUT)

# Extended necessity terms
build_nec <- function(fs_c, fs_t, fs_k, fs_out) {
  nec_df <- data.frame(
    C      = fs_c,
    `~C`   = 1 - fs_c,
    T      = fs_t,
    `~T`   = 1 - fs_t,
    K      = fs_k,
    `~K`   = 1 - fs_k,
    `C+T`  = pmax(fs_c, fs_t),
    `C+K`  = pmax(fs_c, fs_k),
    `T+K`  = pmax(fs_t, fs_k),
    `C+T+K`= pmax(fs_c, fs_t, fs_k),
    OUT    = fs_out,
    check.names = FALSE
  )
  res <- pof(setms = nec_df[, 1:10], outcome = "OUT", data = nec_df, relation = "necessity")
  out <- res$incl.cov
  tibble(
    Expression  = rownames(out),
    Consistency = out[, "inclN"],
    Coverage    = out[, "covN"]
  )
}

nec_old <- build_nec(df$fs_C_old, df$fs_T, df$fs_K, df$fs_OUT) %>% mutate(Model = "C_old")
nec_new <- build_nec(df$fs_C_new, df$fs_T, df$fs_K, df$fs_OUT) %>% mutate(Model = "C_new")
nec_cmp <- bind_rows(nec_old, nec_new) %>%
  pivot_wider(names_from = Model,
              values_from = c(Consistency, Coverage),
              names_sep = " ")

kbl(nec_cmp, digits = 4,
    caption = "Table 7 — Necessity Analysis: C_old vs C_new") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE,
                font_size = 11) %>%
  footnote(general = "'+' = logical OR (disjunction), '~' = negation. Scores ≥ 0.90 bolded.")
```

```{r fig-necessity, fig.cap="Figure 3 — Necessity Consistency: C_old vs C_new"}
nec_plot <- bind_rows(
  nec_old %>% filter(Expression %in% c("C", "T", "K", "C+T", "C+K", "T+K", "C+T+K")),
  nec_new %>% filter(Expression %in% c("C", "T", "K", "C+T", "C+K", "T+K", "C+T+K"))
)

ggplot(nec_plot, aes(x = reorder(Expression, Consistency), y = Consistency,
                     fill = Model)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_hline(yintercept = 0.90, linetype = "dashed", color = "red", linewidth = 0.5) +
  annotate("text", x = 0.6, y = 0.915, label = "0.90 threshold", color = "red",
           hjust = 0, size = 3) +
  coord_flip() +
  scale_fill_manual(values = c("C_old" = "#7570b3", "C_new" = "#1b9e77"),
                    labels = c("C_old" = "NLP prediction (crisp)", "C_new" = "Classifier score (fuzzy)")) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  labs(x = NULL, y = "Necessity Consistency", fill = "Clarity measure") +
  theme(legend.position = "bottom")
```

With the continuous classifier score, $C \cup T$ crosses the necessity
threshold (consistency = **`r sprintf("%.3f", nec_new$Consistency[nec_new$Expression == "C+T"])`**),
while neither condition alone is individually necessary.

## Truth Tables

```{r fsqca-truthtables}
tt_old <- truthTable(qca_old, outcome = "OUT", conditions = c("C", "T", "K"),
                     incl.cut = 0.80, n.cut = 30,
                     sort.by = c("incl", "n"), complete = FALSE)

tt_new <- truthTable(qca_new, outcome = "OUT", conditions = c("C", "T", "K"),
                     incl.cut = 0.80, n.cut = 30,
                     sort.by = c("incl", "n"), complete = FALSE)

format_tt <- function(tt, label) {
  d <- tt$tt
  d %>%
    mutate(
      incl = ifelse(is.na(incl), "—", sprintf("%.4f", as.numeric(incl))),
      PRI  = ifelse(is.na(PRI),  "—", sprintf("%.4f", as.numeric(PRI)))
    ) %>%
    dplyr::select(C, T, K, n, incl, PRI, OUT) %>%
    mutate(Model = label)
}

tt_both <- bind_rows(
  format_tt(tt_old, "C_old (NLP prediction)"),
  format_tt(tt_new, "C_new (classifier score)")
)

kbl(tt_both %>% dplyr::select(-Model),
    col.names = c("C", "T", "K", "N", "Incl.", "PRI", "OUT"),
    caption = "Table 8 — fsQCA Truth Tables (inclusion cut = 0.80, N cut = 30)") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  pack_rows("Panel A: C_old (NLP prediction)", 1, nrow(format_tt(tt_old, ""))) %>%
  pack_rows("Panel B: C_new (classifier score)",
            nrow(format_tt(tt_old, "")) + 1, nrow(tt_both))
```

## Sufficient Configurations

```{r fsqca-minimisation}
sol_old <- tryCatch(minimize(tt_old, details = TRUE), error = function(e) NULL)
sol_new <- tryCatch(minimize(tt_new, details = TRUE), error = function(e) NULL)

format_sol <- function(sol) {
  if (is.null(sol)) return("No sufficient configurations found.")
  paste(capture.output(print(sol)), collapse = "\n")
}
```

### Panel A — C~old~ (NLP prediction)

```{r sol-old, results='asis'}
cat("```\n")
cat(format_sol(sol_old))
cat("\n```\n")
```

### Panel B — C~new~ (classifier score)

```{r sol-new, results='asis'}
cat("```\n")
cat(format_sol(sol_new))
cat("\n```\n")
```

## Sufficiency Consistency Comparison

```{r tbl-suff-compare}
configs <- list(
  "C·T·K" = function(d, c_col) pmin(d[[c_col]], d$fs_T, d$fs_K),
  "C·T"   = function(d, c_col) pmin(d[[c_col]], d$fs_T),
  "C·K"   = function(d, c_col) pmin(d[[c_col]], d$fs_K),
  "T·K"   = function(d, c_col) pmin(d$fs_T, d$fs_K),
  "C"     = function(d, c_col) d[[c_col]],
  "T"     = function(d, c_col) d$fs_T,
  "K"     = function(d, c_col) d$fs_K
)

suff_rows <- lapply(names(configs), function(cfg_name) {
  fn <- configs[[cfg_name]]

  s_old <- fn(df, "fs_C_old")
  cons_old <- sum(pmin(s_old, df$fs_OUT)) / sum(s_old)
  cov_old  <- sum(pmin(s_old, df$fs_OUT)) / sum(df$fs_OUT)

  s_new <- fn(df, "fs_C_new")
  cons_new <- sum(pmin(s_new, df$fs_OUT)) / sum(s_new)
  cov_new  <- sum(pmin(s_new, df$fs_OUT)) / sum(df$fs_OUT)

  tibble(Configuration = cfg_name,
         `Cons (C_old)` = cons_old, `Cov (C_old)` = cov_old,
         `Cons (C_new)` = cons_new, `Cov (C_new)` = cov_new,
         `Δ Cons` = cons_new - cons_old)
})
suff_tbl <- bind_rows(suff_rows)

kbl(suff_tbl, digits = 4,
    caption = "Table 9 — Sufficiency Consistency & Coverage: C_old vs C_new") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE)
```

```{r fig-suff-compare, fig.cap="Figure 4 — Sufficiency Consistency by Configuration (C_old vs C_new)"}
suff_long <- suff_tbl %>%
  dplyr::select(Configuration, `Cons (C_old)`, `Cons (C_new)`) %>%
  pivot_longer(-Configuration, names_to = "Model", values_to = "Consistency") %>%
  mutate(Model = ifelse(Model == "Cons (C_old)", "C_old", "C_new"))

ggplot(suff_long, aes(x = reorder(Configuration, Consistency),
                      y = Consistency, fill = Model)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_hline(yintercept = 0.80, linetype = "dashed", color = "red", linewidth = 0.5) +
  annotate("text", x = 0.6, y = 0.815, label = "0.80 threshold", color = "red",
           hjust = 0, size = 3) +
  coord_flip() +
  scale_fill_manual(values = c("C_old" = "#7570b3", "C_new" = "#1b9e77"),
                    labels = c("C_old" = "NLP prediction (crisp)", "C_new" = "Classifier score (fuzzy)")) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  labs(x = NULL, y = "Sufficiency Consistency", fill = "Clarity measure") +
  theme(legend.position = "bottom")
```

# Summary of Findings

```{r tbl-synthesis}
synth <- tibble(
  Evidence = c(
    "Main Poisson (IDL → Y)",
    "OLS",
    "Ordered logit",
    "Provider FE Poisson",
    "Legacy binary J_i",
    "Quintile Q5 vs Q1",
    "fsQCA C·T·K (C_new)"
  ),
  `Effect Size` = c(
    sprintf("IRR = %.3f", irr),
    sprintf("β = %.3f", ols_b),
    sprintf("OR = %.3f", exp(ologit_b)),
    sprintf("IRR = %.3f", exp(pfe_b)),
    sprintf("IRR = %.3f", exp(ji_b)),
    sprintf("IRR = %.3f", exp(q5_b)),
    sprintf("Cons. = %.3f", suff_tbl$`Cons (C_new)`[suff_tbl$Configuration == "C·T·K"])
  ),
  Significant = c(
    "Yes (p < .001)", "Yes (p < .001)", "Yes (p < .001)",
    ifelse(pfe_p < 0.05, "Yes", "No"),
    ifelse(ji_p < 0.05, "Yes", "No"),
    ifelse(q5_p < 0.05, "Yes", "No"),
    ifelse(suff_tbl$`Cons (C_new)`[suff_tbl$Configuration == "C·T·K"] >= 0.75,
           "Above 0.75 cut", "Below 0.75 cut")
  ),
  `Method` = c("Poisson PML", "OLS", "Ordered Logit", "Poisson + FE",
               "Poisson PML", "Poisson PML", "fsQCA (set-theoretic)")
)

kbl(synth,
    caption = "Table 10 — Convergent Evidence: All Approaches Point in the Same Direction") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE)
```

## Methodological Recommendation

**Main specification → Poisson regression** (Table 3). This provides a clear,
single estimate of the IDL–liquidity relationship with standard inferential
support (SE, CI, p-value), controls for use-case composition and provider
heterogeneity, and yields a directly interpretable effect size (IRR).

**Robustness → fsQCA** (Section 5). The configurational analysis complements
the regression by (a) operating under a fundamentally different analytical logic
(set-theoretic rather than correlational), (b) revealing equifinal pathways, and
(c) demonstrating that using the continuous classifier score instead of the binary
prediction eliminates the theoretically inconsistent substitution patterns that
previously afflicted the QCA results.

*Both approaches converge:* higher IDL is associated with more transactional-readiness
signals, whether assessed as an average marginal effect or as a sufficient
configurational recipe.
