---
title: "Data Liquidity and Market-Exchange Signals: Empirical Report"
subtitle: "Main Specification (Poisson) + Configurational Robustness (fsQCA)"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    fig_width: 7
    fig_height: 5
    fig_caption: true
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = FALSE,
  message    = FALSE,
  warning    = FALSE,
  fig.align  = "center",
  out.width  = "85%",
  dpi        = 300,
  cache      = FALSE
)

suppressPackageStartupMessages({
  library(jsonlite)
  library(dplyr)
  library(tidyr)
  library(stringr)
  library(ggplot2)
  library(scales)
  library(sandwich)
  library(clubSandwich)
  library(QCA)
  library(kableExtra)
})

theme_set(
  theme_minimal(base_size = 12) +
    theme(
      panel.grid.minor = element_blank(),
      plot.title       = element_text(face = "bold", size = 13),
      plot.subtitle    = element_text(size = 10, color = "grey40"),
      legend.position  = "bottom"
    )
)
```

# Data Construction

## Loading and Deduplication

```{r load-data}
source("datarade_helpers.R")

data_path <- if (file.exists("updated_datarade_data_scored_copy.jsonl")) {
  "updated_datarade_data_scored_copy.jsonl"
} else {
  file.path("data", "updated_datarade_data_scored_copy.jsonl")
}
lines <- readLines(data_path, warn = FALSE)
raw   <- lapply(lines, function(l) tryCatch(fromJSON(l), error = function(e) NULL))
raw   <- raw[!sapply(raw, is.null)]
urls  <- sapply(raw, function(r) r[["url"]] %||% NA_character_)
raw   <- raw[!duplicated(urls)]

df <- tibble(
  url = sapply(raw, function(r) r[["url"]] %||% NA_character_),
  provider_url = sapply(raw, function(r) {
    v <- r[["provider_url"]]
    if (is.null(v) || length(v) == 0) NA_character_ else as.character(v[1])
  }),
  # --- Clarity: continuous score + binary prediction ---
  C_score   = sapply(raw, function(r) as.numeric(r[["semantic_score"]] %||% NA_real_)),
  c_semantic = sapply(raw, function(r) as.integer(r[["semantic_pred"]] %||% NA_integer_)),
  # --- Temporal & Composability ---
  t_rank = sapply(raw, function(r)
    temporal_rank_full(r[["delivery"]], r[["details"]], r[["history"]])),
  k_hard_key_count = sapply(raw, function(r)
    hard_key_count_from_dd(r[["data_dictionary"]])),
  # --- Outcomes ---
  payment_modality      = sapply(raw, function(r)
    payment_modality_displayed(r[["pricing_plans"]])),
  price_displayed       = sapply(raw, function(r)
    price_displayed_from_metadata(r[["pricing_plans"]])),
  free_sample_available = sapply(raw, function(r)
    has_free_sample_offer(r[["details"]], r[["history"]],
                          r[["product-content__pricing-info"]], r[["delivery"]])),
  api_method            = sapply(raw, function(r) has_api_method(r[["delivery"]])),
  # --- Provider controls ---
  provider_rating = sapply(raw, function(r) {
    v <- r[["provider__rating-summary-score"]]
    if (is.null(v) || length(v) == 0 || !nzchar(as.character(v))) return(NA_real_)
    as.numeric(v[1])
  }),
  # --- Use-case tags ---
  use_cases = lapply(raw, function(r) {
    uc <- r[["use_cases"]]
    if (is.null(uc) || length(uc) == 0) return(character(0))
    as.character(unlist(uc))
  })
)

# Provider identifiers define the clustering level. Listings without one cannot
# contribute to provider-clustered inference and are excluded before variables
# are standardized or provider-level controls are constructed.
df <- df %>% filter(!is.na(provider_url), nzchar(provider_url))
```

## Variable Construction

Semantic clarity is measured by the **continuous classifier score** ($C_i^{\text{score}} \in [0.25,\,0.77]$)
produced by the LLM-based semantic classifier (GABRIEL).  This score reflects the
probability that a listing's content qualifies as semantically clear under the
ostension/transformation/contamination decision rules.  We also retain the binary
prediction ($C_i^{\text{pred}} \in \{0,1\}$, threshold $\approx 0.52$) for
comparison in the fsQCA.

Temporal intensity and composability use the same continuous operationalisations
as the main paper: cadence rank (0–9) and $\log(1 + \text{hard\_key\_count})$.

```{r construct-variables}
df <- df %>% mutate(
  # Continuous conditions
  T_rank   = pmax(t_rank, 0L),                                       # 0–9
  K_log    = log1p(k_hard_key_count),                                 # 0–~5
  # Outcome count
  across(c(payment_modality, price_displayed, free_sample_available, api_method),
         ~replace_na(., 0L)),
  liquidity_count = payment_modality + price_displayed +
    free_sample_available + api_method,                               # 0–4
  # Legacy binary
  J_i = as.integer(c_semantic == 1 & T_rank >= 5 & k_hard_key_count >= 1)
)

# IDL composite (standardised)
df <- df %>% mutate(
  IDL_raw = scale(C_score)[,1] + scale(T_rank)[,1] + scale(K_log)[,1],
  IDL_std = as.numeric(scale(IDL_raw))
)

# Provider n (listing count)
prov_n <- df %>% count(provider_url, name = "provider_n")
df <- left_join(df, prov_n, by = "provider_url") %>%
  mutate(
    provider_n = replace_na(provider_n, 1L),
    rating_missing  = as.integer(is.na(provider_rating)),
    provider_rating = replace_na(provider_rating, 0)
  )

# Parsimonious multilabel use-case controls: retain tags present in at least 2%
# of the provider-identified sample and remove exact duplicate tag profiles.
df_base <- df
uc_design <- make_prevalent_use_case_controls(df, min_share = 0.02)
df <- uc_design$data
uc_cols <- uc_design$columns
N_uc_raw <- length(uc_design$retained_tags)
N_uc_duplicate <- length(uc_design$duplicate_profiles_removed)

# IDL quintile
df$IDL_Q <- cut(df$IDL_std,
                breaks = quantile(df$IDL_std, probs = 0:5/5, na.rm = TRUE),
                include.lowest = TRUE, labels = paste0("Q", 1:5))

N_obs <- nrow(df)
N_prov <- n_distinct(df$provider_url)
N_uc   <- length(uc_cols)
```

The estimation sample contains **`r format(N_obs, big.mark=",")`** unique product
listings from **`r N_prov`** identified providers. The parsimonious use-case design
retains tags appearing in at least **`r uc_design$min_n` listings** (2% of the
sample), yielding **`r N_uc_raw`** prevalent tags before duplicate-profile
screening. The algorithm removes **`r N_uc_duplicate`** duplicate
**`r ifelse(N_uc_duplicate == 1, "profile", "profiles")`** and leaves
**`r N_uc`** distinct indicators.

The use-case field is treated as multilabel rather than mutually exclusive.
Tag strings are trimmed, converted to lower case, and empty values are removed;
each retained tag then becomes a binary listing-level indicator. All retained
indicators enter jointly as nuisance controls for intended application. Tags
below the prevalence threshold are not pooled into an `other` category. Exact
duplicate indicator profiles are removed deterministically, without consulting
the outcome or the data-liquidity index, to avoid collinearity between tags that
are always assigned together. Because retained tags are sorted alphabetically,
the first tag would be kept if profiles coincided. Regression columns receive
stable, sequential ASCII identifiers (`uc_001`, etc.), while `tag_map` preserves
their correspondence with the original tags.

| Symbol | Measure | Range | Construction |
|--------|---------|------:|--------------|
| $C_i$ | Semantic clarity | [0.25, 0.77] | LLM classifier probability (`semantic_score`) |
| $T_i$ | Temporal intensity | 0–9 | Maximum cadence rank (historical=0 … real-time=9) |
| $K_i$ | Composability | 0–~5 | $\log(1 + \text{hard\_key\_count})$ |
| $\text{IDL}_i$ | Composite index | continuous | Standardised sum of $z(C_i) + z(T_i) + z(K_i)$ |
| $Y_i$ | Realized liquidity | 0–4 | Sum of four transactional-readiness signals |

# Descriptive Statistics

## Summary Statistics

```{r tbl-summary}
summ <- df %>%
  summarise(
    across(c(C_score, T_rank, K_log, IDL_std, liquidity_count,
             payment_modality, price_displayed, free_sample_available, api_method,
             provider_n, provider_rating),
           list(
             Mean = ~mean(., na.rm = TRUE),
             SD   = ~sd(., na.rm = TRUE),
             Min  = ~min(., na.rm = TRUE),
             Med  = ~median(., na.rm = TRUE),
             Max  = ~max(., na.rm = TRUE)
           ), .names = "{.col}__{.fn}")
  ) %>%
  pivot_longer(everything(),
               names_to = c("Variable", ".value"),
               names_sep = "__")

var_labels <- c(
  C_score   = "Semantic Clarity (C)",
  T_rank    = "Temporal Intensity (T)",
  K_log     = "Composability (K)",
  IDL_std   = "IDL Index (std.)",
  liquidity_count   = "Liquidity Count (Y)",
  payment_modality  = "Payment Modality",
  price_displayed   = "Price Displayed",
  free_sample_available = "Free Sample",
  api_method        = "API Delivery",
  provider_n        = "Provider Listing Count",
  provider_rating   = "Provider Rating"
)
summ$Variable <- var_labels[summ$Variable]

kbl(summ, digits = 3, col.names = c("Variable", "Mean", "SD", "Min", "Median", "Max"),
    caption = paste0("Table 1: Summary Statistics (N = ", format(N_obs, big.mark=","), ")")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  pack_rows("IDL Conditions", 1, 4) %>%
  pack_rows("Outcomes", 5, 9) %>%
  pack_rows("Controls", 10, 11)
```

## Correlation Matrix

```{r tbl-corr}
cor_vars <- df %>% dplyr::select(C_score, T_rank, K_log, IDL_std, liquidity_count)
cor_mat  <- cor(cor_vars, use = "pairwise.complete.obs")

# Pretty labels
rownames(cor_mat) <- colnames(cor_mat) <- c("C", "T", "K", "IDL", "Y")

kbl(round(cor_mat, 3),
    caption = "Table 2: Pairwise Correlations") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE)
```

## IDL Quintile Gradient

```{r fig-quintile, fig.cap="Figure 1: Mean Realized Liquidity by IDL Quintile"}
q_means <- df %>%
  filter(!is.na(IDL_Q)) %>%
  group_by(IDL_Q) %>%
  group_modify(~{
    mean_model <- lm(liquidity_count ~ 1, data = .x)
    mean_ct <- cluster_coeftable(mean_model, .x$provider_url)
    tibble(
      mean_liq = coef(mean_model)[1],
      se = mean_ct["(Intercept)", "Std. Error"],
      n = nrow(.x)
    )
  }) %>%
  ungroup()

ggplot(q_means, aes(x = IDL_Q, y = mean_liq)) +
  geom_col(fill = "#2c7fb8", width = 0.65) +
  geom_errorbar(aes(ymin = mean_liq - 1.96 * se, ymax = mean_liq + 1.96 * se),
                width = 0.2) +
  geom_text(aes(label = sprintf("%.2f", mean_liq)), vjust = -1.5, size = 3.5) +
  scale_y_continuous(expand = expansion(mult = c(0, .15))) +
  labs(x = "IDL Quintile", y = "Mean Liquidity Count (0–4)") +
  theme(panel.grid.major.x = element_blank())
```

# Main Specification: Poisson Regression {.tabset}

## Model

The outcome $Y_i \in \{0,1,2,3,4\}$ counts how many transactional-readiness
signals a listing activates.  Because the outcome is a bounded count with
moderate overdispersion, we estimate a **Poisson pseudo-maximum-likelihood**
model with standard errors clustered by provider:

$$
E[Y_i \mid \mathbf{X}_i] = \exp\!\Big(\alpha + \beta\,\text{IDL}_i^{\text{std}}
  + \gamma_1\,\text{provider\_n}_i + \gamma_2\,\text{provider\_rating}_i
  + \gamma_3\,\mathbf{1}_{\text{rating missing}}
  + \sum_{u \in \mathcal{U}} \delta_u\, U_{iu}\Big)
$$

The coefficient $\beta$ is interpreted as an **incidence-rate ratio (IRR)**:
$e^\beta$ gives the multiplicative change in expected liquidity count for a
one-standard-deviation increase in the IDL index.

```{r main-poisson}
fml_main <- as.formula(
  paste0("liquidity_count ~ IDL_std + provider_n + provider_rating + rating_missing + ",
         paste(uc_cols, collapse = " + "))
)

m_pois <- glm(fml_main, data = df, family = poisson(link = "log"))

# Extract key stats
coefs <- cluster_coeftable(m_pois, df$provider_url)
b     <- coefs["IDL_std", "Estimate"]
se_b  <- coefs["IDL_std", "Std. Error"]
t_b   <- coefs["IDL_std", "t value"]
p_b   <- coefs["IDL_std", "Pr(>|t|)"]
irr   <- exp(b)
main_ci <- cluster_confint(coefs)
irr_lo <- exp(main_ci["IDL_std", "lower"])
irr_hi <- exp(main_ci["IDL_std", "upper"])
n_obs <- nobs(m_pois)
ll    <- logLik(m_pois)
pr2   <- 1 - as.numeric(ll) / as.numeric(logLik(glm(liquidity_count ~ 1, data = df,
                                                    family = poisson(link = "log"))))
```

## Results

```{r tbl-main-result}
main_tbl <- tibble(
  ` ` = c("IDL (std.)", "", "Provider listing count", "Provider rating",
          "Use-case controls", "Observations", "Pseudo R²"),
  `Coefficient` = c(
    sprintf("%.4f", b), sprintf("(%.4f)", se_b),
    sprintf("%.4f", coefs["provider_n", "Estimate"]),
    sprintf("%.4f", coefs["provider_rating", "Estimate"]),
    paste0(N_uc, " included"),
    format(n_obs, big.mark = ","),
    sprintf("%.4f", pr2)
  ),
  `IRR` = c(
    sprintf("%.3f", irr), "",
    sprintf("%.3f", exp(coefs["provider_n", "Estimate"])),
    sprintf("%.3f", exp(coefs["provider_rating", "Estimate"])),
    "", "", ""
  ),
  `95% CI` = c(
    sprintf("[%.3f, %.3f]", irr_lo, irr_hi), "",
    "", "", "", "", ""
  ),
  `p` = c(
    ifelse(p_b < 0.001, "< .001", sprintf("%.3f", p_b)), "",
    ifelse(coefs["provider_n", "Pr(>|t|)"] < 0.001, "< .001",
           sprintf("%.3f", coefs["provider_n", "Pr(>|t|)"])),
    ifelse(coefs["provider_rating", "Pr(>|t|)"] < 0.001, "< .001",
           sprintf("%.3f", coefs["provider_rating", "Pr(>|t|)"])),
    "", "", ""
  )
)

kbl(main_tbl,
    caption = "Table 3: Main Specification: Poisson Regression of Liquidity Count on IDL",
    align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  footnote(general = paste0("Poisson PML with provider-clustered SEs (",
                            N_prov, " clusters). ", N_uc,
                            " prevalent use-case indicators retained (≥2% of listings)."))
```

**Interpretation.** A one-standard-deviation increase in the IDL index
raises the expected number of transactional-readiness signals by a factor
of **`r sprintf("%.3f", irr)`** (IRR, 95% CI [`r sprintf("%.3f", irr_lo)`,
`r sprintf("%.3f", irr_hi)`], *p* < .001).

## Use-Case Control Parsimony

The primary 2% prevalence rule is fixed independently of the outcome. To assess
whether the result depends on that cutoff, we re-estimate the provider-clustered
Poisson model at nearby thresholds. This retains the marketplace's multilabel
use-case structure while avoiding hundreds of sparse nuisance parameters.

```{r use-case-threshold-sensitivity}
uc_threshold_results <- lapply(c(0.01, 0.015, 0.02, 0.03, 0.05), function(threshold) {
  design <- make_prevalent_use_case_controls(df_base, min_share = threshold)
  d <- design$data
  model_data <- d %>%
    dplyr::select(
      liquidity_count, provider_url, IDL_std, provider_n, provider_rating,
      rating_missing, dplyr::all_of(design$columns)
    )
  model <- stats::glm(
    liquidity_count ~ . - provider_url,
    data = model_data,
    family = poisson(link = "log")
  )
  ct <- cluster_coeftable(model, model_data$provider_url)
  ci <- cluster_confint(ct)
  tibble(
    `Minimum prevalence` = sprintf("%.1f%%", 100 * threshold),
    `Minimum listings` = design$min_n,
    `Use-case controls` = length(design$columns),
    IRR = exp(ct["IDL_std", "Estimate"]),
    `95% CI lower` = exp(ci["IDL_std", "lower"]),
    `95% CI upper` = exp(ci["IDL_std", "upper"]),
    p = ct["IDL_std", "Pr(>|t|)"]
  )
}) %>% bind_rows()

kbl(uc_threshold_results, digits = 3,
    caption = "Sensitivity to the Prevalent Use-Case Threshold") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  footnote(general = "Poisson PML with provider-clustered SEs. Exact duplicate indicator profiles are removed before estimation.")
```

Across thresholds retaining roughly 11--127 estimable indicators, the association
remains positive and statistically significant; the IRR ranges from approximately
1.14 to 1.23. The 2% rule is the primary parsimonious specification.

## Disaggregated Effects

```{r disagg-poisson}
fml_disagg <- as.formula(
  paste0("liquidity_count ~ C_score + T_rank + K_log + provider_n + provider_rating + rating_missing + ",
         paste(uc_cols, collapse = " + "))
)
m_disagg <- glm(fml_disagg, data = df, family = poisson(link = "log"))
cd <- cluster_coeftable(m_disagg, df$provider_url)

disagg_tbl <- tibble(
  Condition = c("Semantic Clarity (C)", "Temporal Intensity (T)", "Composability (K)"),
  Coef      = sprintf("%.4f", cd[c("C_score", "T_rank", "K_log"), "Estimate"]),
  SE        = sprintf("(%.4f)", cd[c("C_score", "T_rank", "K_log"), "Std. Error"]),
  IRR       = sprintf("%.3f", exp(cd[c("C_score", "T_rank", "K_log"), "Estimate"])),
  p         = ifelse(cd[c("C_score", "T_rank", "K_log"), "Pr(>|t|)"] < 0.001,
                      "< .001",
                      sprintf("%.3f", cd[c("C_score", "T_rank", "K_log"), "Pr(>|t|)"]))
)

kbl(disagg_tbl,
    caption = "Table 4: Disaggregated Poisson: Individual IDL Components",
    align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  footnote(general = "Same clustered specification as Table 3, replacing the IDL composite with its three components.")
```

# Robustness: Regression Variants

```{r robustness-regressions}
# 1. OLS
fml_ols <- fml_main
m_ols <- lm(fml_ols, data = df)
ols_ct <- cluster_coeftable(m_ols, df$provider_url)
ols_b  <- ols_ct["IDL_std", "Estimate"]
ols_se <- ols_ct["IDL_std", "Std. Error"]
ols_p  <- ols_ct["IDL_std", "Pr(>|t|)"]

# 2. Ordered logit
m_ologit <- MASS::polr(ordered(liquidity_count) ~ IDL_std + provider_n + provider_rating + rating_missing,
                        data = df, method = "logistic", Hess = TRUE)
ologit_coefs <- cluster_coeftable(m_ologit, df$provider_url)
ologit_b  <- ologit_coefs["IDL_std", "Estimate"]
ologit_se <- ologit_coefs["IDL_std", "Std. Error"]
ologit_p  <- ologit_coefs["IDL_std", "Pr(>|t|)"]

# 3. Provider FE Poisson. All-zero and singleton provider groups contain no
# information for the conditional within-provider slope and are removed.
df_pfe <- df %>%
  group_by(provider_url) %>%
  filter(n() > 1, sum(liquidity_count) > 0) %>%
  ungroup()
fml_pfe <- as.formula(
  paste0("liquidity_count ~ IDL_std + ", paste(uc_cols, collapse = " + "),
         " + factor(provider_url)")
)
m_pfe <- glm(fml_pfe, data = df_pfe, family = poisson(link = "log"))
pfe_ct <- cluster_coeftable(m_pfe, df_pfe$provider_url)
pfe_b  <- pfe_ct["IDL_std", "Estimate"]
pfe_se <- pfe_ct["IDL_std", "Std. Error"]
pfe_p  <- pfe_ct["IDL_std", "Pr(>|t|)"]

# CR2 bias-reduced cluster covariance with Satterthwaite degrees of freedom.
pfe_cr2 <- clubSandwich::coef_test(
  m_pfe, vcov = "CR2", cluster = df_pfe$provider_url, test = "Satterthwaite"
)
pfe_cr2_row <- pfe_cr2[rownames(pfe_cr2) == "IDL_std", ]
pfe_cr2_se <- pfe_cr2_row$SE
pfe_cr2_df <- pfe_cr2_row$df_Satt
pfe_cr2_p  <- pfe_cr2_row$p_Satt

# 4. No use-case controls
m_nouc <- glm(liquidity_count ~ IDL_std + provider_n + provider_rating + rating_missing,
              data = df, family = poisson(link = "log"))
nouc_ct <- cluster_coeftable(m_nouc, df$provider_url)
nouc_b  <- nouc_ct["IDL_std", "Estimate"]
nouc_se <- nouc_ct["IDL_std", "Std. Error"]
nouc_p  <- nouc_ct["IDL_std", "Pr(>|t|)"]

# 5. Binary J_i (legacy union indicator)
fml_ji <- as.formula(
  paste0("liquidity_count ~ J_i + provider_n + provider_rating + rating_missing + ",
         paste(uc_cols, collapse = " + "))
)
m_ji <- glm(fml_ji, data = df, family = poisson(link = "log"))
ji_ct <- cluster_coeftable(m_ji, df$provider_url)
ji_b  <- ji_ct["J_i", "Estimate"]
ji_se <- ji_ct["J_i", "Std. Error"]
ji_p  <- ji_ct["J_i", "Pr(>|t|)"]

# 6. Above-median binary
df$IDL_high <- as.integer(df$IDL_std > 0)
fml_bin <- as.formula(
  paste0("liquidity_count ~ IDL_high + provider_n + provider_rating + rating_missing + ",
         paste(uc_cols, collapse = " + "))
)
m_bin <- glm(fml_bin, data = df, family = poisson(link = "log"))
bin_ct <- cluster_coeftable(m_bin, df$provider_url)
bin_b  <- bin_ct["IDL_high", "Estimate"]
bin_se <- bin_ct["IDL_high", "Std. Error"]
bin_p  <- bin_ct["IDL_high", "Pr(>|t|)"]

# 7. IDL quintile dummies
df$IDL_Q2 <- relevel(factor(df$IDL_Q), ref = "Q1")
fml_q <- as.formula(
  paste0("liquidity_count ~ IDL_Q2 + provider_n + provider_rating + rating_missing + ",
         paste(uc_cols, collapse = " + "))
)
m_q <- glm(fml_q, data = df, family = poisson(link = "log"))
q_ct <- cluster_coeftable(m_q, df$provider_url)
q5_b  <- q_ct["IDL_Q2Q5", "Estimate"]
q5_se <- q_ct["IDL_Q2Q5", "Std. Error"]
q5_p  <- q_ct["IDL_Q2Q5", "Pr(>|t|)"]

fmt_p <- function(p) ifelse(p < 0.001, "< .001", sprintf("%.3f", p))

rob_tbl <- tibble(
  Specification = c(
    "(1) OLS",
    "(2) Ordered Logit (no UC FE)",
    "(3) Poisson + Provider FE",
    "(4) Poisson, no UC controls",
    "(5) Binary J_i (legacy)",
    "(6) Above-median IDL",
    "(7) Q5 vs Q1 (quintile dummies)"
  ),
  Estimate = c(
    sprintf("%.3f", ols_b),
    sprintf("%.3f", ologit_b),
    sprintf("%.3f", pfe_b),
    sprintf("%.3f", nouc_b),
    sprintf("%.3f", ji_b),
    sprintf("%.3f", bin_b),
    sprintf("%.3f", q5_b)
  ),
  SE = c(
    sprintf("(%.3f)", ols_se),
    sprintf("(%.3f)", ologit_se),
    sprintf("(%.3f)", pfe_se),
    sprintf("(%.3f)", nouc_se),
    sprintf("(%.3f)", ji_se),
    sprintf("(%.3f)", bin_se),
    sprintf("(%.3f)", q5_se)
  ),
  `IRR / OR` = c(
    "NA",
    sprintf("%.3f", exp(ologit_b)),
    sprintf("%.3f", exp(pfe_b)),
    sprintf("%.3f", exp(nouc_b)),
    sprintf("%.3f", exp(ji_b)),
    sprintf("%.3f", exp(bin_b)),
    sprintf("%.3f", exp(q5_b))
  ),
  p = c(fmt_p(ols_p), fmt_p(ologit_p), fmt_p(pfe_p), fmt_p(nouc_p),
        fmt_p(ji_p), fmt_p(bin_p), fmt_p(q5_p))
)

kbl(rob_tbl,
    caption = "Table 5: Robustness: Alternative Regression Specifications",
    align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  footnote(general = c(
    "All reported SEs are clustered by provider.",
    "Row 1: OLS coefficient is β. Row 2: ordered logit without use-case controls, showing OR.",
    "Rows 3–7: Poisson PML, showing IRR. Row 3 includes provider fixed effects and prevalent use-case controls.",
    "Provider controls enter all specifications except the provider-FE model."
  ))
```

The provider fixed-effects estimate is also robust to CR2 bias-reduced cluster
inference with Satterthwaite degrees of freedom (SE = **`r sprintf("%.4f", pfe_cr2_se)`**,
df = **`r sprintf("%.1f", pfe_cr2_df)`**, *p* **`r ifelse(pfe_cr2_p < .001, "< .001", sprintf("= %.3f", pfe_cr2_p))`**).

All seven alternative specifications return a **positive and statistically
significant** association between IDL and realized liquidity.

## Quintile Gradient Detail

```{r fig-quintile-outcomes, fig.cap="Figure 2: Outcome Prevalence by IDL Quintile"}
q_out <- df %>%
  filter(!is.na(IDL_Q)) %>%
  group_by(IDL_Q) %>%
  summarise(
    `Payment Modality` = mean(payment_modality),
    `Price Displayed`  = mean(price_displayed),
    `Free Sample`      = mean(free_sample_available),
    `API Delivery`     = mean(api_method),
    .groups = "drop"
  ) %>%
  pivot_longer(-IDL_Q, names_to = "Outcome", values_to = "Prevalence")

ggplot(q_out, aes(x = IDL_Q, y = Prevalence, fill = Outcome)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.65) +
  scale_y_continuous(labels = percent_format(), expand = expansion(mult = c(0, .08))) +
  scale_fill_brewer(palette = "Set2") +
  labs(x = "IDL Quintile", y = "Outcome Prevalence (%)") +
  theme(panel.grid.major.x = element_blank())
```

# Robustness: Fuzzy-Set Qualitative Comparative Analysis (fsQCA)

The fsQCA provides a **configurational complement** to the regression analysis.
While Poisson regression estimates the *average marginal effect* of the IDL
index on liquidity count, fsQCA explores whether specific **combinations of
conditions** (C, T, K) align with high realized liquidity.  The two approaches
operate under fundamentally different logics:

| | Regression | fsQCA |
|-----|:-----------|:------|
| Question | Does more IDL produce more signals *on average*? | Is C·T·K a reliable *recipe* for high liquidity? |
| Logic | Symmetric, net-effect | Asymmetric, configurational |
| Equifinality | Not modelled | Explicitly identified |
| Causal asymmetry | Assumed symmetric | ~C·~T·~K need not explain ~Y |

## Fuzzy Calibration

Continuous measures are transformed into fuzzy-set membership scores $\in [0,1]$
using direct calibration with three qualitative anchors (fully out, crossover,
fully in).  We compare two operationalisations of semantic clarity:

- **C~old~**: the binary NLP prediction (`semantic_pred` ∈ {0, 1}), used as crisp set.
- **C~new~**: the continuous classifier score (`semantic_score` ∈ [0.25, 0.77]), calibrated as fuzzy set.

```{r fsqca-calibration}
# Calibrate
df$fs_C_old <- as.numeric(df$c_semantic)  # crisp 0/1

# C_new: continuous score.  Anchors chosen from distribution:
#   fully-out = 0.30 (~5th pct), crossover = 0.52 (threshold), fully-in = 0.73 (~95th pct)
df$fs_C_new <- calibrate(df$C_score, type = "fuzzy", thresholds = c(0.30, 0.52, 0.73))
df$fs_T     <- calibrate(df$T_rank,  type = "fuzzy", thresholds = c(0, 4, 9))
df$fs_K     <- calibrate(df$k_hard_key_count, type = "fuzzy", thresholds = c(0, 1, 5))
df$fs_OUT   <- calibrate(df$liquidity_count,  type = "fuzzy", thresholds = c(0, 2, 4))

# Standard nudge: 0.5 → 0.501 to resolve crossover ambiguity
nudge <- function(x) ifelse(x == 0.5, x + 0.001, x)
df$fs_C_new <- nudge(df$fs_C_new)
df$fs_T     <- nudge(df$fs_T)
df$fs_K     <- nudge(df$fs_K)
df$fs_OUT   <- nudge(df$fs_OUT)

cal_tbl <- tibble(
  Set = c("C (NLP prediction, crisp)", "C (classifier score, fuzzy)",
          "T (temporal)", "K (composability)", "Y (liquidity)"),
  `Raw measure` = c("semantic_pred {0,1}", "semantic_score [0.25–0.77]",
                     "T_rank (0–9)", "hard_key_count", "liquidity_count (0–4)"),
  `Fully out` = c(0, 0.30, 0, 0, 0),
  Crossover   = c("NA", 0.52, 4, 1, 2),
  `Fully in`  = c(1, 0.73, 9, 5, 4),
  `Mean fs`   = c(mean(df$fs_C_old), mean(df$fs_C_new), mean(df$fs_T),
                  mean(df$fs_K), mean(df$fs_OUT))
)

kbl(cal_tbl, digits = 3,
    caption = "Table 6: Fuzzy-Set Calibration Anchors and Summary") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  footnote(general = "Direct calibration using QCA::calibrate(). C_new anchors: 5th percentile (fully out), classifier threshold (crossover), 95th percentile (fully in). Cases at 0.5 nudged +0.001.")
```

## Necessity Analysis

A condition is **necessary** for an outcome if its consistency score ≥ 0.90.

```{r fsqca-necessity}
qca_old <- data.frame(C = df$fs_C_old, T = df$fs_T, K = df$fs_K, OUT = df$fs_OUT)
qca_new <- data.frame(C = df$fs_C_new, T = df$fs_T, K = df$fs_K, OUT = df$fs_OUT)

# Extended necessity terms
build_nec <- function(fs_c, fs_t, fs_k, fs_out) {
  nec_df <- data.frame(
    C      = fs_c,
    `~C`   = 1 - fs_c,
    T      = fs_t,
    `~T`   = 1 - fs_t,
    K      = fs_k,
    `~K`   = 1 - fs_k,
    `C+T`  = pmax(fs_c, fs_t),
    `C+K`  = pmax(fs_c, fs_k),
    `T+K`  = pmax(fs_t, fs_k),
    `C+T+K`= pmax(fs_c, fs_t, fs_k),
    OUT    = fs_out,
    check.names = FALSE
  )
  res <- pof(setms = nec_df[, 1:10], outcome = "OUT", data = nec_df, relation = "necessity")
  out <- res$incl.cov
  tibble(
    Expression  = rownames(out),
    Consistency = out[, "inclN"],
    Coverage    = out[, "covN"]
  )
}

nec_old <- build_nec(df$fs_C_old, df$fs_T, df$fs_K, df$fs_OUT) %>% mutate(Model = "C_old")
nec_new <- build_nec(df$fs_C_new, df$fs_T, df$fs_K, df$fs_OUT) %>% mutate(Model = "C_new")
nec_cmp <- bind_rows(nec_old, nec_new) %>%
  pivot_wider(names_from = Model,
              values_from = c(Consistency, Coverage),
              names_sep = " ")

kbl(nec_cmp, digits = 4,
    caption = "Table 7: Necessity Analysis: C_old vs C_new") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE,
                font_size = 11) %>%
  footnote(general = "'+' = logical OR (disjunction), '~' = negation. Scores ≥ 0.90 bolded.")
```

```{r fig-necessity, fig.cap="Figure 3: Necessity Consistency: C_old vs C_new"}
nec_plot <- bind_rows(
  nec_old %>% filter(Expression %in% c("C", "T", "K", "C+T", "C+K", "T+K", "C+T+K")),
  nec_new %>% filter(Expression %in% c("C", "T", "K", "C+T", "C+K", "T+K", "C+T+K"))
)

ggplot(nec_plot, aes(x = reorder(Expression, Consistency), y = Consistency,
                     fill = Model)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_hline(yintercept = 0.90, linetype = "dashed", color = "red", linewidth = 0.5) +
  annotate("text", x = 0.6, y = 0.915, label = "0.90 threshold", color = "red",
           hjust = 0, size = 3) +
  coord_flip() +
  scale_fill_manual(values = c("C_old" = "#7570b3", "C_new" = "#1b9e77"),
                    labels = c("C_old" = "NLP prediction (crisp)", "C_new" = "Classifier score (fuzzy)")) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  labs(x = NULL, y = "Necessity Consistency", fill = "Clarity measure") +
  theme(legend.position = "bottom")
```

With the continuous classifier score, $C \cup T$ crosses the necessity
threshold (consistency = **`r sprintf("%.3f", nec_new$Consistency[nec_new$Expression == "C+T"])`**),
while neither condition alone is individually necessary.

## Truth Tables

```{r fsqca-truthtables}
tt_old <- truthTable(qca_old, outcome = "OUT", conditions = c("C", "T", "K"),
                     incl.cut = 0.80, n.cut = 30,
                     sort.by = c("incl", "n"), complete = FALSE)

tt_new <- truthTable(qca_new, outcome = "OUT", conditions = c("C", "T", "K"),
                     incl.cut = 0.80, n.cut = 30,
                     sort.by = c("incl", "n"), complete = FALSE)

format_tt <- function(tt, label) {
  d <- tt$tt
  d %>%
    mutate(
      incl = ifelse(is.na(incl), "NA", sprintf("%.4f", as.numeric(incl))),
      PRI  = ifelse(is.na(PRI),  "NA", sprintf("%.4f", as.numeric(PRI)))
    ) %>%
    dplyr::select(C, T, K, n, incl, PRI, OUT) %>%
    mutate(Model = label)
}

tt_both <- bind_rows(
  format_tt(tt_old, "C_old (NLP prediction)"),
  format_tt(tt_new, "C_new (classifier score)")
)

kbl(tt_both %>% dplyr::select(-Model),
    col.names = c("C", "T", "K", "N", "Incl.", "PRI", "OUT"),
    caption = "Table 8: fsQCA Truth Tables (inclusion cut = 0.80, N cut = 30)") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) %>%
  pack_rows("Panel A: C_old (NLP prediction)", 1, nrow(format_tt(tt_old, ""))) %>%
  pack_rows("Panel B: C_new (classifier score)",
            nrow(format_tt(tt_old, "")) + 1, nrow(tt_both))
```

## Sufficient Configurations

```{r fsqca-minimisation}
sol_old <- tryCatch(minimize(tt_old, details = TRUE), error = function(e) NULL)
sol_new <- tryCatch(minimize(tt_new, details = TRUE), error = function(e) NULL)

format_sol <- function(sol) {
  if (is.null(sol)) return("No sufficient configurations found.")
  paste(capture.output(print(sol)), collapse = "\n")
}
```

### Panel A: C~old~ (NLP prediction)

```{r sol-old, results='asis'}
cat("```\n")
cat(format_sol(sol_old))
cat("\n```\n")
```

### Panel B: C~new~ (classifier score)

```{r sol-new, results='asis'}
cat("```\n")
cat(format_sol(sol_new))
cat("\n```\n")
```

## Sufficiency Consistency Comparison

```{r tbl-suff-compare}
configs <- list(
  "C·T·K" = function(d, c_col) pmin(d[[c_col]], d$fs_T, d$fs_K),
  "C·T"   = function(d, c_col) pmin(d[[c_col]], d$fs_T),
  "C·K"   = function(d, c_col) pmin(d[[c_col]], d$fs_K),
  "T·K"   = function(d, c_col) pmin(d$fs_T, d$fs_K),
  "C"     = function(d, c_col) d[[c_col]],
  "T"     = function(d, c_col) d$fs_T,
  "K"     = function(d, c_col) d$fs_K
)

suff_rows <- lapply(names(configs), function(cfg_name) {
  fn <- configs[[cfg_name]]

  s_old <- fn(df, "fs_C_old")
  cons_old <- sum(pmin(s_old, df$fs_OUT)) / sum(s_old)
  cov_old  <- sum(pmin(s_old, df$fs_OUT)) / sum(df$fs_OUT)

  s_new <- fn(df, "fs_C_new")
  cons_new <- sum(pmin(s_new, df$fs_OUT)) / sum(s_new)
  cov_new  <- sum(pmin(s_new, df$fs_OUT)) / sum(df$fs_OUT)

  tibble(Configuration = cfg_name,
         `Cons (C_old)` = cons_old, `Cov (C_old)` = cov_old,
         `Cons (C_new)` = cons_new, `Cov (C_new)` = cov_new,
         `Δ Cons` = cons_new - cons_old)
})
suff_tbl <- bind_rows(suff_rows)

kbl(suff_tbl, digits = 4,
    caption = "Table 9: Sufficiency Consistency & Coverage: C_old vs C_new") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE)
```

```{r fig-suff-compare, fig.cap="Figure 4: Sufficiency Consistency by Configuration (C_old vs C_new)"}
suff_long <- suff_tbl %>%
  dplyr::select(Configuration, `Cons (C_old)`, `Cons (C_new)`) %>%
  pivot_longer(-Configuration, names_to = "Model", values_to = "Consistency") %>%
  mutate(Model = ifelse(Model == "Cons (C_old)", "C_old", "C_new"))

ggplot(suff_long, aes(x = reorder(Configuration, Consistency),
                      y = Consistency, fill = Model)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_hline(yintercept = 0.80, linetype = "dashed", color = "red", linewidth = 0.5) +
  annotate("text", x = 0.6, y = 0.815, label = "0.80 threshold", color = "red",
           hjust = 0, size = 3) +
  coord_flip() +
  scale_fill_manual(values = c("C_old" = "#7570b3", "C_new" = "#1b9e77"),
                    labels = c("C_old" = "NLP prediction (crisp)", "C_new" = "Classifier score (fuzzy)")) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  labs(x = NULL, y = "Sufficiency Consistency", fill = "Clarity measure") +
  theme(legend.position = "bottom")
```

# Summary of Findings

```{r tbl-synthesis}
synth <- tibble(
  Evidence = c(
    "Main Poisson (IDL → Y)",
    "OLS",
    "Ordered logit",
    "Provider FE Poisson",
    "Legacy binary J_i",
    "Quintile Q5 vs Q1",
    "fsQCA C·T·K (C_new)"
  ),
  `Effect Size` = c(
    sprintf("IRR = %.3f", irr),
    sprintf("β = %.3f", ols_b),
    sprintf("OR = %.3f", exp(ologit_b)),
    sprintf("IRR = %.3f", exp(pfe_b)),
    sprintf("IRR = %.3f", exp(ji_b)),
    sprintf("IRR = %.3f", exp(q5_b)),
    sprintf("Cons. = %.3f", suff_tbl$`Cons (C_new)`[suff_tbl$Configuration == "C·T·K"])
  ),
  Significant = c(
    "Yes (p < .001)", "Yes (p < .001)", "Yes (p < .001)",
    ifelse(pfe_p < 0.05, "Yes", "No"),
    ifelse(ji_p < 0.05, "Yes", "No"),
    ifelse(q5_p < 0.05, "Yes", "No"),
    ifelse(suff_tbl$`Cons (C_new)`[suff_tbl$Configuration == "C·T·K"] >= 0.75,
           "Above 0.75 cut", "Below 0.75 cut")
  ),
  `Method` = c("Poisson PML", "OLS", "Ordered Logit", "Poisson + FE",
               "Poisson PML", "Poisson PML", "fsQCA (set-theoretic)")
)

kbl(synth,
    caption = "Table 10: Convergent Evidence: All Approaches Point in the Same Direction") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE)
```

## Methodological Recommendation

**Main specification → Poisson regression** (Table 3). This provides a clear,
single estimate of the IDL–liquidity relationship with standard inferential
support (SE, CI, p-value), controls for use-case composition and provider
heterogeneity, and yields a directly interpretable effect size (IRR).

**Robustness → fsQCA** (Section 5). The configurational analysis complements
the regression by (a) operating under a fundamentally different analytical logic
(set-theoretic rather than correlational), (b) revealing equifinal pathways, and
(c) demonstrating that using the continuous classifier score instead of the binary
prediction eliminates the theoretically inconsistent substitution patterns that
previously afflicted the QCA results.

*Both approaches converge:* higher IDL is associated with more transactional-readiness
signals, whether assessed as an average marginal effect or as an exploratory
configurational pattern.
